Bird beak's elaboration and innovation

### 2023-06-19 Analysis/07-Orthogonality_and_statistics.Rmd
reinstall

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
#TODO: make the groups nested in the fable
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14, 3, 5)]

@@

pdf("../Manuscript/Figures/orthogonality_results.pdf", width = 9, height = 9)
plot.orthogonality(super_orders, orders_n2, orders, col = gg.color.hue(4)[1:2])
legend("topleft", legend = c("Super-orders (vs. phylogeny)", "Orders (vs. phylogeny)", "Orders (vs. super-orders)"), col = c(gg.color.hue(4)[1], gg.color.hue(4)[2], adjustcolor(gg.color.hue(4)[2], alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8, bty = "n")
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
## Same but for the passeriformes
pdf("../Manuscript/Figures/orthogonality_results_passeriformes.pdf", width = 9, height = 9)
plot.orthogonality(sub_orders, families_n2, families, col = gg.color.hue(4)[3:4])
legend("topleft", legend = c("Sub-orders (vs. passeriformes)", "Families (vs. sub-orders)", "Families (vs. passeriformes)"), col = c(gg.color.hue(4)[3], gg.color.hue(4)[4], adjustcolor(gg.color.hue(4)[4], alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8, bty = "n")
dev.off()
```

@@

## Distribution of elaboration and innovation at the clade level
scale.group <- function(X) return(X/max(X))
elaboration_super_orders <- lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), scale.group)
innovation_super_orders  <- lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), scale.group)
elaboration_orders       <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
innovation_orders        <- lapply(get.disparity(results$order_results_between$distance, concatenate = FALSE), scale.group)

## The objects above are the ones that contain all the elaboration and innovation values by clade level
## These bits are for the Bhatt coeff
elaboration_group <- rbind(do.call(rbind, elaboration_super_orders), do.call(rbind, elaboration_orders))
innovation_group <- rbind(do.call(rbind, innovation_super_orders), do.call(rbind, innovation_orders))

## Measuring the area under the curves (for the Bhatt coeff)
elaboration_species_auc <- apply(elaboration_species, 2, area.density)
innovation_species_auc  <- apply(innovation_species, 2, area.density)
elaboration_group_auc   <- apply(elaboration_group, 2, area.density)
innovation_group_auc    <- apply(innovation_group, 2, area.density)

@@

elab <- 
  ggplot(fake, aes(x = elaboration, colour=Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("yellow", "purple")) +
  xlab("Relative elaboration") +
  ylab("Density") +
  theme(legend.position = "none") +
  labs(tags="a")

innov <-
  ggplot(fake, aes(x = innovation, colour = Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("yellow", "purple")) +
  xlab("Relative innovation") + 
  theme(legend.position = c(0.8, 0.8)) +
  labs(tags="b")

@@

ggsave("../Manuscript/Figures/relative_EI_gg_style_unscaled.pdf", plot=p, height=6, width=12)
```

@@

## Getting the group pairs
group_pairs <- sapply(name.subsets(all_birds_shapespace)[-36], function(x) c(x, "phylogeny"), simplify = FALSE)

## Calculating the random skewers for each group
skewers_r <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun), between.groups = group_pairs, verbose = TRUE)
skewers_p <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun.p), between.groups = group_pairs, verbose = TRUE)

@@

col <- rev(c(rep(gg.color.hue(4)[1], 8), rep(gg.color.hue(4)[2], 27)))

par(mar = c(5, 17, 4, 2))
plot(NULL, xlim = c(0, 1), ylim = c(1,length(skewers_distrib)), xlab = "Skewers correlation", ylab = "", yaxt = "n")
abline(v = 0.5, lty = 2, col = "grey", lwd = 0.5)
axis(2, at = length(skewers_distrib):1, labels = plot_names, las = 2)
## Skewers
for(i in length(skewers_distrib):1) {
    lines(x = skewers_distrib[i][[1]][c(2, 5)], y = rep(i, 2), lty = 2, lwd = 1, col = col[i])
    lines(x = skewers_distrib[i][[1]][c(3, 4)], y = rep(i, 2), lty = 1, lwd = 2, col = col[i])
    points(x = skewers_distrib[i][[1]][1], y = i, pch = 19, col = col[i])
    text(x = skewers_distrib[i][[1]][1]+0.03, y = i+0.2, label = p.star(skewers_median_p[[i]]), col = col[i])
}

>>>>

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14, 3, 5)]

@@

pdf("../Manuscript/Figures/orthogonality_results.pdf", width = 9, height = 9)
plot.orthogonality(super_orders, orders_n2, orders, col = c("purple", "#FBB117"))
legend("topleft", legend = c("Super-orders (vs. phylogeny)", "Orders (vs. phylogeny)", "Orders (vs. super-orders)"), col = c("purple", "#FBB117", adjustcolor("#FBB117", alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8, bty = "n")
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
## Same but for the passeriformes
pdf("../Manuscript/Figures/orthogonality_results_passeriformes.pdf", width = 9, height = 9)
plot.orthogonality(sub_orders, families_n2, families, col =c("purple", "#FBB117"))
legend("topleft", legend = c("Sub-orders (vs. passeriformes)", "Families (vs. sub-orders)", "Families (vs. passeriformes)"), col = c("purple", "#FBB117", adjustcolor("#FBB117", alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8, bty = "n")
dev.off()
```

@@

## Distribution of elaboration and innovation at the clade level
scale.group <- function(X) return(X/quantile(X, prob = 0.975)[1])
elaboration_super_orders <- lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), scale.group)
innovation_super_orders  <- lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), scale.group)
elaboration_orders       <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
innovation_orders        <- lapply(get.disparity(results$order_results_between$distance, concatenate = FALSE), scale.group)

## RAM cleaning
rm(results)

## The objects above are the ones that contain all the elaboration and innovation values by clade level
## These bits are for the Bhatt coeff
# elaboration_group <- rbind(do.call(rbind, elaboration_super_orders), do.call(rbind, elaboration_orders))
# innovation_group <- rbind(do.call(rbind, innovation_super_orders), do.call(rbind, innovation_orders))

## Measuring the area under the curves (for the Bhatt coeff)
# elaboration_species_auc <- apply(elaboration_species, 2, area.density)
# innovation_species_auc  <- apply(innovation_species, 2, area.density)
# elaboration_group_auc   <- apply(elaboration_group, 2, area.density)
# innovation_group_auc    <- apply(innovation_group, 2, area.density)

@@

elab <- 
  ggplot(fake, aes(x = elaboration, colour=Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("#FBB117", "purple")) +
  xlab("Relative elaboration") +
  ylab("Density") +
  theme(legend.position = "none") +
  labs(tags="a")

innov <-
  ggplot(fake, aes(x = innovation, colour = Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("#FBB117", "purple")) +
  xlab("Relative innovation") + 
  theme(legend.position = c(0.8, 0.8)) +
  labs(tags="b")

@@

ggsave("../Manuscript/Figures/relative_EI_gg_style_95CIscaled.pdf", plot=p, height=6, width=12)
```

@@

## Getting the group pairs
group_pairs <- sapply(name.subsets(all_birds_shapespace)[-36], function(x) c(x, "phylogeny"), simplify = FALSE)
group_pairs_orders <- list(
    "Galliformes" = c("Galliformes", "Galloanserae"),
    "Accipitriformes" = c("Accipitriformes", "Telluraves"),
    "Strigiformes" = c("Strigiformes", "Telluraves"),
    "Musophagiformes" = c("Musophagiformes", "Aequornithes"),
    "Trogoniformes" = c("Trogoniformes", "Telluraves"),
    "Columbiformes" = c("Columbiformes", "Columbimorphae"),
    "Caprimulgiformes" = c("Caprimulgiformes", "Strisores"),
    "Bucerotiformes" = c("Bucerotiformes", "Telluraves"),
    "Falconiformes" = c("Falconiformes", "Telluraves"),
    "Pterocliformes" = c("Pterocliformes", "Columbimorphae"),
    "Sphenisciformes" = c("Sphenisciformes", "Aequornithes"),
    "Podicipediformes" = c("Podicipediformes", "Mirandornithes"),
    "Ciconiiformes" = c("Ciconiiformes", "Aequornithes"),
    "Tinamiformes" = c("Tinamiformes", "Paleognathae"),
    "Suliformes" = c("Suliformes", "Aequornithes"),
    "Anseriformes" = c("Anseriformes", "Galloanserae"),
    "Apodiformes" = c("Apodiformes", "Strisores"),
    "Otidiformes" = c("Otidiformes", "Otidimorphae"),
    "Cuculiformes" = c("Cuculiformes", "Otidimorphae"),
    "Psittaciformes" = c("Psittaciformes", "Telluraves"),
    "Pelecaniformes" = c("Pelecaniformes", "Aequornithes"),
    "Procellariiformes" = c("Procellariiformes", "Aequornithes"),
    "Piciformes" = c("Piciformes", "Telluraves"),
    "Passeriformes" = c("Passeriformes", "Telluraves"),
    "Coraciiformes" = c("Coraciiformes", "Telluraves"))

## Calculating the random skewers for each group
skewers_r <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun), between.groups = group_pairs, verbose = TRUE)
skewers_p <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun.p), between.groups = group_pairs, verbose = TRUE)
skewers_r_order <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun), between.groups = group_pairs_orders, verbose = TRUE)
skewers_p_order <- dispRity(all_birds_shapespace, metric = as.covar(skewers.fun.p), between.groups = group_pairs_orders, verbose = TRUE)

@@

## Same but for the orders
skewers_distrib_order <- lapply(get.disparity(skewers_r_order, concatenate = FALSE), quantile, probs = c(0.5, 0.025, 0.25, 0.75, 0.975))
skewers_median_p_order <- lapply(get.disparity(skewers_p_order, concatenate = FALSE), median)
plot_names_order <- unlist(lapply(strsplit(names(skewers_distrib_order), split = ":"), `[[`, 1))
names(skewers_distrib_order) <- names(skewers_median_p_order) <- plot_names_order

## Set the colours to match the ones from the ortho figure
col <- c(rep("purple", 8), rep("#FBB117", 27))

pdf(height = 12, width = 7, file = "../Manuscript/Figures/random_skewers.pdf")
par(mar = c(5, 17, 4, 2))
plot(NULL, xlim = c(0, 1), ylim = c(length(skewers_distrib),1), xlab = "Skewers correlation", ylab = "", yaxt = "n")
abline(v = 0.5, lty = 2, col = "grey", lwd = 0.5)
axis(2, at = 1:length(skewers_distrib), labels = plot_names, las = 2)
## Skewers
for(i in length(skewers_distrib):1) {
    lines(x = skewers_distrib[i][[1]][c(2, 5)], y = rep(i, 2), lty = 2, lwd = 1, col = col[i])
    lines(x = skewers_distrib[i][[1]][c(3, 4)], y = rep(i, 2), lty = 1, lwd = 2, col = col[i])
    points(x = skewers_distrib[i][[1]][1], y = i, pch = 19, col = col[i])
    text(x = skewers_distrib[i][[1]][1]+0.03, y = i-0.2, label = p.star(skewers_median_p[[i]]), col = col[i])
    ## Add orders (if available)
    if(names(skewers_distrib)[i] %in% plot_names_order) {
        n <- which(names(skewers_distrib)[i] == plot_names_order)
        col_n <- adjustcolor(col[i], alpha = 1/2)
        ## Plotting the order-superorder level results
        lines(x = skewers_distrib_order[n][[1]][c(2, 5)], y = rep(i, 2)+0.2, lty = 3, lwd = 1, col = col_n)
        lines(x = skewers_distrib_order[n][[1]][c(3, 4)], y = rep(i, 2)+0.2, lty = 1, lwd = 2, col = col_n)
        points(x = skewers_distrib_order[n][[1]][1], y = i+0.2, pch = 21, col = col_n)
        text(x = skewers_distrib_order[n][[1]][1]+0.03, y = i, label = p.star(skewers_median_p_order[[n]]), col = col_n)
    }
}
dev.off()
```

### 2023-06-19 Analysis/09-Figure_key.Rmd
reinstall

## Creating the subsets
superorder_shapespace <- MCMCglmm.subsets(n = 4000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(super_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

@@

## Get projection lines
get.proj.line <- function(point, base) {
  point <- t(point)
  base <- t(base)
  proj_x <- ( (point[1]*base[1] + point[2]*base[2]) / (base[1]*base[1] + base[2]*base[2]) ) * base[1];
  proj_y <- ( (point[1]*base[1] + point[2]*base[2]) / (base[1]*base[1] + base[2]*base[2]) ) * base[2];
  return(rbind(cbind(proj_x, proj_y), point))
}

## Projection onto the phylo line
pdf("../Manuscript/Figures/figure_key_projection_on_phylo.pdf")
plot(NULL, xlab = "PC1", ylab = "PC2", xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5))
# lines(base_vector)
for(i in 1:nrow(matrix)) {
      lines(get.proj.line(matrix[i, ], base_vectors$phylogeny[[1]]))
}
points(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)], col = gg.color.hue(1), pch = 19)
covar.plot(space_paleo,
      col = c("grey", gg.color.hue(1)),
      ellipses = mean,
      major.axes = mean,
      legend = FALSE,
      points = FALSE,
      cex = 0.5, apply.to.VCV = TRUE,
      lwd = 4,
      add = TRUE,
      scale = 2)
dev.off()

## Projection onto the group line
pdf("../Manuscript/Figures/figure_key_projection_on_group.pdf")
plot(NULL, xlab = "PC1", ylab = "PC2", xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5))
points(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)], col = gg.color.hue(1), pch = 19)

base <- base_vectors$Paleognathae[[1]]
# base <- matrix(c(base)[c(1, 1, 4, 4)], 2, 2, byrow = FALSE) # or c(1, 4, 3, 2)
for(i in 1:nrow(matrix)) {
      lines(get.proj.line(matrix[i, ], base))
}

points(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)], col = gg.color.hue(1), pch = 19)
covar.plot(space_paleo,
      col = c("grey", gg.color.hue(1)),
      ellipses = mean,
      major.axes = mean,
      legend = FALSE,
      points = FALSE,
      cex = 0.5, apply.to.VCV = TRUE,
      lwd = 4,
      add = TRUE,
      scale = 2)
dev.off()

@@

## Get the data (in the right order)
load("../Data/Processed/ploting_data.rda")
elaborations <- ploting_data$median_elaborations[tree_paleo$tip.label]
innovations <- ploting_data$median_innovations[tree_paleo$tip.label]

@@

pdf("../Manuscript/Figures/figure_key_tree_example2.pdf")
plot(ladderize(tree_paleo), show.tip.label = FALSE)
dev.off()

```

>>>>

## Creating the subsets
superorder_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(super_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

@@

## Get projection lines
get.proj.line <- function(point, base, just.proj = FALSE) {
  point <- t(point)
  base <- t(base)
  proj_x <- ( (point[1]*base[1] + point[2]*base[2]) / (base[1]*base[1] + base[2]*base[2]) ) * base[1];
  proj_y <- ( (point[1]*base[1] + point[2]*base[2]) / (base[1]*base[1] + base[2]*base[2]) ) * base[2];
  if(just.proj) {
      return(cbind(proj_x, proj_y))
  } else {
      return(rbind(cbind(proj_x, proj_y), point))
  }
}
get.any.proj.lines <- function(points, base) {
      ## 1 - Get the coordinates of the points
      points_coords <- points[, ]
            # points(points_coords, col = "grey")
      ## 2 - Get the coordinates of the base
      base_coords <- base
            # lines(base_coords, col = "grey")

      ## 3 - translate the points and base onto the origin of the base
      translation_vector <- c(0, 0) - base_coords[2,]
      points_coords_translated <- t(t(points_coords) + translation_vector)
      base_coords_translated <- t(t(base_coords) + translation_vector)
            # lines(base_coords_translated)
            # points(points_coords_translated)

      ## 4 - project all the translated points onto the translated base
      lines_out_translated <- t(apply(points_coords_translated, 1, get.proj.line, base = base_coords_translated, just.proj = TRUE))
            # lines(rbind(lines_out_translated[1, ], points_coords_translated[1, ]))

      ## 5 - untranslate the points
      lines_out <- t(t(lines_out_translated) - translation_vector)
            # lines(rbind(lines_out[1, ], points_coords[1, ]), col = "red")
      return(lines_out)
}

## Projection onto the phylo line
pdf("../Manuscript/Figures/figure_key_projection_on_phylo.pdf")
plot(NULL, xlab = "PC1", ylab = "PC2", xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5))
## Project all the points on the base line
proj_points <- get.any.proj.lines(matrix, base = base_vectors$phylogeny[[1]])
## Plot all these lines
for(i in 1:nrow(matrix)) {
    lines(rbind(matrix[i, ], proj_points[i, ]), col = "grey")
}
## Add the points
points(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)], col = gg.color.hue(1), pch = 19)
## Add the ellipses
covar.plot(space_paleo,
      col = c("grey", gg.color.hue(1)),
      ellipses = mean,
      major.axes = mean,
      legend = FALSE,
      points = FALSE,
      cex = 0.5, apply.to.VCV = TRUE,
      lwd = 4,
      add = TRUE,
      scale = 2)
dev.off()

## Projection onto the group line
pdf("../Manuscript/Figures/figure_key_projection_on_group.pdf")
plot(NULL, xlab = "PC1", ylab = "PC2", xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5))
## Project all the points on the base line
proj_points <- get.any.proj.lines(matrix, base = base_vectors$Paleognathae[[1]])
## Plot all these lines
for(i in 1:nrow(matrix)) {
    lines(rbind(matrix[i, ], proj_points[i, ]), col = gg.color.hue(1))
}
## Add the points
points(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)], col = gg.color.hue(1), pch = 19)
## Add the ellipses
covar.plot(space_paleo,
      col = c("grey", gg.color.hue(1)),
      ellipses = mean,
      major.axes = mean,
      legend = FALSE,
      points = FALSE,
      cex = 0.5, apply.to.VCV = TRUE,
      lwd = 4,
      add = TRUE,
      scale = 2)
dev.off()

@@

## Get the data (in the right order)
load("../Data/Processed/ploting_data_order.rda")
elaborations <- ploting_data_order$median_elaborations[tree_paleo$tip.label]
innovations <- ploting_data_order$median_innovations[tree_paleo$tip.label]

@@

# Focal species is Dromaius
```

### 2023-06-19 Analysis/11-sensitivity_analysis.Rmd
reinstall

```{r, eval = FALSE, echo = FALSE}
## Random space
BMspace_models_names <- model_files[grep("BMspace", model_files)]
## Models placeholder
BMspace_models <- list()

@@

<!-- Figure 9: BMised shapespace mcmcmcglmmm diagnosis -->

@@

@@

@@

```{r, eval = FALSE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Cluster/shapespace_charadriiformes/BMspace_charadriiformes_1.mini.chains")
shapespace <- BMspace_charadriiformes_$data
## Get the posteriors
load(file = "../Data/Processed/BMspace_charadriiformes_posteriors.MCMCglmm")

@@

>>>>

```{r, eval = TRUE, echo = FALSE}
## Random space
BMspace_models_names <- model_files[grep("BMspace", model_files)]
## Models placeholder
BMspace_models <- list()

@@

Figure 9: BMised shapespace mcmcmcglmmm diagnosis

@@

Figure 10: the VCV matrices from the original shapespace.

@@

Figure 11: the VCV matrices from the balled shapespace.

@@

Figure 12: the VCV matrices from the randomised shapespace.

```{r, eval = TRUE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Cluster/shapespace_charadriiformes/BMspace_charadriiformes_1.mini.chains")
shapespace <- BMspace_charadriiformes_$data
## Get the posteriors
load(file = "../Data/Processed/BMspace_charadriiformes_posteriors.MCMCglmm")

@@

Figure 13: the VCV matrices from the original shapespace.

## Projection analyses

```{r, eval = FALSE, echo = FALSE}
## Getting all the projections
get.all.projetion.analyses <- function(space) {
      all_results <- list()
      all_results$groups <-  dispRity.covar.projections(space,
                                            type = "groups",
                                            base = "phylogeny",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
      all_results$proj_phylo <- dispRity.covar.projections(space,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
      all_results$proj_group <- dispRity.covar.projections(space,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
      return(all_results)
}

shapespace_results <- get.all.projetion.analyses(chara_shapespace)
ballspace_results <- get.all.projetion.analyses(chara_ballspace)
randospace_results <- get.all.projetion.analyses(chara_randospace)
BMspace_results <- get.all.projetion.analyses(chara_BMspace)

sensitivity_results <- list("original"   = shapespace_results,
                            "balled"     = ballspace_results,
                            "randomised" = randospace_results,
                            "BMised"     = BMspace_results)
save(sensitivity_results, file = "../Data/Processed/sensitivity_results.rda")
```

```{r, eval = TRUE, echo = FALSE}
## Loading the results
library(dispRity)
source("../Functions/ploting.utilities.R")
source("../Functions/correlations.utilities.R")
load("../Data/Processed/sensitivity_results.rda")

## Getting the average projection/rejections
original_proj_phylo <- get.correlations(sensitivity_results$original$proj_phylo)
ballspace_proj_phylo <- get.correlations(sensitivity_results$balled$proj_phylo)
randospace_proj_phylo <- get.correlations(sensitivity_results$randomised$proj_phylo)
BMspace_proj_phylo <- get.correlations(sensitivity_results$BMised$proj_phylo)
original_proj_group <- get.correlations(sensitivity_results$original$proj_group)
ballspace_proj_group <- get.correlations(sensitivity_results$balled$proj_group)
randospace_proj_group <- get.correlations(sensitivity_results$randomised$proj_group)
BMspace_proj_group <- get.correlations(sensitivity_results$BMised$proj_group)

## Plotting the original space
plot.cor <- function(data, col = col_vector, ...) {
      data <- lapply(data, function(x) return(x[c(1,2)]))
      range <- range(unlist(data))
      plot(NULL, xlim = range, ylim = range, xlab = "elaboration", ylab = "innovation", ...)
      abline(v = 1, lty = 2)
      abline(h = 1, lty = 2)
      points(data[[1]], col = col[1], pch = 19)
      points(data[[2]], col = col[2], pch = 19)
      points(data[[3]], col = col[3], pch = 19)
}

col_vector <- rev(c("blue", "darkgreen", "orange"))
par(mfrow = c(2,2))
plot.cor(original_proj_phylo, main = "Original space")
plot.cor(ballspace_proj_phylo, main = "Balled space")
plot.cor(randospace_proj_phylo, main = "Random space")
plot.cor(BMspace_proj_phylo, main = "BM space")

Figure 14: comparison between the different space modifications

```{r, eval = TRUE, echo = FALSE}
## Loading the results
par(mfrow = c(2,2))
plot.cor(original_proj_group, main = "Original space (macro level)")
plot.cor(ballspace_proj_group, main = "Balled space (macro level)")
plot.cor(randospace_proj_group, main = "Random space (macro level)")
plot.cor(BMspace_proj_group, main = "BM space (macro level)")
```

Figure 15: comparison between the different space modifications (when projecting onto their ownb group)

```{r, eval = FALSE, echo = FALSE}
par(mfrow = c(2,2))
## Get the scaling the variance of each dimension
ballspace <- shapespace
ballspace[, selected_dim] <- apply(shapespace[, selected_dim], 2, scale)

## Comparing D1 and D3 for the contrast
png("balling_effect.png", height = 8, width = 8)
par(mfrow = c(2,2))
plot(shapespace[, c(1,3)], xlab = write.pc(1, shape_var_prop), ylab = write.pc(3, shape_var_prop),
      xlim = range.axis(shapespace, selected_dim), ylim = range.axis(shapespace, selected_dim),
      main = "Original shapespace", pch = 19,
      col = c("orange", "blue", "darkgreen")[as.numeric(shapespace$level)])
legend("bottomrigh", pch = 19, legend = c("gulls", "plovers", "sandpipers"), col= c("orange", "blue", "darkgreen"))

plot(ballspace[, c(1,3)], xlab = write.pc(1, ball_var_prop), ylab = write.pc(3, ball_var_prop),
      xlim = c(-4, 4), ylim = c(-4, 4),
      main = "Balled shapespace", pch = 19,
      col = c("orange", "blue", "darkgreen")[as.numeric(shapespace$level)])
plot.cor(original_proj_phylo, main = "Original space")
plot.cor(ballspace_proj_phylo, main = "Balled space")
dev.off()
```

### 2023-06-19 Analysis/14-Elab_innov_through_time.Rmd
reinstall

pdf(height = 14, width = 7, file = "../Manuscript/Figures/Elaboration_and_innovation_clade_through_time.pdf")
par(mfrow = c(2,1))
plot.age.data(elaboration_plot_data, ylab = "Elaboration", xlab = "", main = "Clade's elaboration/innovation\nthrough time")
legend("topleft", pch = 21, col = unlist(orders_elaboration$col), legend = rownames(orders_elaboration), cex = 0.7)
legend("top", pch = 19, col = unlist(super_orders_elaboration$col), legend = rownames(super_orders_elaboration), cex = 0.7)
plot.age.data(innovation_plot_data, ylab = "Innovation", xlab = "Time (Mya)")
dev.off()
```

@@

pdf(height = 14, width = 7, file = "../Manuscript/Figures/Elaboration_and_innovation_species_through_time.pdf")
par(mfrow = c(2,1))
plot.age.data(elaboration_plot_data, ylab = "Elaboration", xlab = "", main = "Species's elaboration/innovation\nthrough time (per clade)")
legend("topright", pch = 21, col = unlist(orders_elaboration$col), legend = unlist(orders_elaboration$subsets), cex = 0.7)
legend("top", pch = 19, col = unlist(super_orders_elaboration$col), legend = unlist(super_orders_elaboration$subsets), cex = 0.7)
plot.age.data(innovation_plot_data, ylab = "Innovation", xlab = "Time (Mya)")
dev.off()
```

>>>>

pdf(height = 7, width = 14, file = "../Manuscript/Figures/Elaboration_and_innovation_clade_through_time.pdf")
par(mfrow = c(1,2))
plot.age.data(elaboration_plot_data, ylab = expression('elaboration'['clade']), xlab = "Time (Mya)", main = "")
legend("topleft", pch = 21, col = unlist(orders_elaboration$col), legend = rownames(orders_elaboration), cex = 0.7)
legend("top", pch = 19, col = unlist(super_orders_elaboration$col), legend = rownames(super_orders_elaboration), cex = 0.7)
plot.age.data(innovation_plot_data, ylab = expression('innovation'['clade']), xlab = "Time (Mya)")
dev.off()
```

@@

pdf(height = 7, width = 14, file = "../Manuscript/Figures/Elaboration_and_innovation_species_through_time.pdf")
par(mfrow = c(1,2))
plot.age.data(elaboration_plot_data, ylab = expression('elaboration'['species']), xlab = "Time (Mya)", main = "")
legend("topright", pch = 21, col = unlist(orders_elaboration$col), legend = unlist(orders_elaboration$subsets), cex = 0.7)
legend("top", pch = 19, col = unlist(super_orders_elaboration$col), legend = unlist(super_orders_elaboration$subsets), cex = 0.7)
plot.age.data(innovation_plot_data, ylab = expression('innovation'['species']), xlab = "Time (Mya)")
dev.off()
```
